Truth space method for caching database queries

### 2015-03-01 english_version/MAIS/paper_main.tex
MAIS version was added. Codd OLAP citation was removed from all versions.

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\author{Mosin Sergey, Zykin Sergey}
\usepackage{amssymb,amsmath}
\usepackage{amsthm}
%\usepackage{amsfonts}
%\usepackage{algorithm}
%\usepackage{xcolor}
%\usepackage{textcomp}
\newtheorem{note}{Note}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{statement}{Statement}
\def \eval #1#2{\left.#1\right\vert_{#2}}
\def \<#1> {\langle #1 \rangle}
\def \n #1{\mathit{#1}}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Theoretical Computer Science}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Truth space method for caching database queries}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{S.~V. Mosin, S.~V. Zykin}

\address{Sobolev Institute of Mathematics of the Siberian Branch
of the Russian Academy of Sciences}

\begin{abstract}
We propose a new method of client-side data caching for relational databases
with a central server and distant clients. Data is loaded into client cache
based on queries executed on the central database at the server. These
queries have a special form - "universal relational query". The majority of
search queries to database can be expressed in such form. Besides, this form
allows us to analyze query correctness by checking lossless join property. A
subsequent query may be executed in client's local cache if we can determine
that the query result is entirely contained in the cache. For this we compare
truth spaces of the logical restrictions in new user's query and results of
the queries execution in cache. This method may be used to define lacking data
in cache and execute the query on server for this data only. Problem of data
actualizations in cache is not discussed in this paper. However, it can be
solved by cataloging of queries on server and their serving by triggers in
background mode.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword  keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
Relational databases \sep Caching \sep Truth space
\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
In this paper we discuss the use of data views that are
cached on the client's computer. We assume client-server environment with
server based Relational Database (RDB). The cache stores query results in order
to provide maximum usage of saved data in subsequent queries.

@@

% Head 1
\section{Existing solutions overview and comparison}
One of the main research problems of queries optimization to database is the
construction of an optimal query plan. Queries are transformed without content
analysis of the database content and cache. In other cases, this information is
taken into account for calculation statistical estimations to improve physical
access to data. These problems are the subject of many studies, but they are
outside of our approach.

@@

\section{Acknowledgements}
This work is supported by the Russian Foundation for Basic Research under
grant \#12-07-00066-a.

\bibliographystyle{elsarticle-num}
\bibliography{references}

>>>>

\documentclass{maiseng}

\author{Mosin Sergey, Zykin Sergey}

\usepackage[cp1251]{inputenc}
\usepackage[english,russian]{babel}
\usepackage[T2A]{fontenc}
\usepackage{amssymb,amsmath}
\usepackage{amsthm}

\selectlanguage{english}

%%
\date{April 15, }\ydate{2013}
\firstpage{175}

\renewcommand{\refname}{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Macros used in the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newtheorem{note}{Note}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{statement}{Statement}
\def \eval #1#2{\left.#1\right\vert_{#2}}
\def \<#1> {\langle #1 \rangle}
\def \n #1{\mathit{#1}}

\addto\captionsrussian{\renewcommand*{\proofname}{Proof}}

%%%%%%%%%%%%%%%%%% end my macros %%%%%%%%%%%%%%%%%%%

%%
\title{Truth space method for caching database queries}
\author{Mosin~S.~V., Zykin~S.~V.\footnote{Supported by the Russian Foundation for Basic Research under
grant \#12-07-00066-a.}}
\authorcr{Mosin~S.~V., Zykin~S.~V.}
\keywords{Relational databases, Caching, Truth space}
\rutitle{Кэширование запросов к реляционной базе данных с использованием областей истинности}
\ruauthor{Мосин С.В., Зыкин С.В.}

\rukeywords{реляционная база данных, кэш, область истинности}

\UDC{519.987} \shorttitle{Truth space method for caching database queries}
\affiliation{\small Sobolev Institute of Mathematics of the Siberian Branch
of the Russian Academy of Sciences, \\Pevtsova str., 13, Omsk, 644043, Russia}
\ruaffiliation{\small Омский филиал Федерального государственного бюджетного учреждения науки Института математики им. С.Л.~Соболева Сибирского отделения Российской академии наук \\644043, Россия, г. Омск,
ул. Певцова, 13,}
%%%%
\email{svmosin@gmail.com, szykin@mail.ru}
\authorinform{
\textbf{Мосин Сергей Владимирович},\\Омский филиал Федерального государственного бюджетного учреждения науки Института математики им. С.Л.~Соболева Сибирского отделения Российской академии наук, аспирант\\
\textbf{Зыкин Сергей Владимирович},\\Омский филиал Федерального государственного бюджетного учреждения науки Института математики им. С.Л.~Соболева Сибирского отделения Российской академии наук, д-р техн. наук, профессор
}

\ruabstract{
В данной статье предлагается новый метод кэширования запросов к реляционной базе данных
для систем с центральным сервером и распределенными клиентами. Данные загружаются в
клиентский кэш, основываясь на запросах, выполненных на сервере БД. Эти запросы имеют специальный вид, называемый "универсальный реляционный запрос". Большинство запросов может быть записано в этом виде. Кроме того, эта форма записи позволяет анализировать корректность запроса, проверяя свойство соединения без потери информации (СБПИ). Последовательные запросы могут исполняться на клиенте, используя кэш, если удастся определить, что результаты искомого запроса полностью содержатся в кэше. Для осуществления такой проверки анализируются области истинности логических ограничений искомого запроса и запросов, результаты которых уже содержатся в кэше. Этот метод может быть использован для определения недостающих в кэше данных и последующего запроса только на эти данные. Проблема актуализации данных не затрагивается в этой статье. Однако она может быть решена путем учета запросов на сервере и обновлении данных при помощи триггеров.}

\begin{document}
\maketitle

\begin{abstract}
We propose a new method of client-side data caching for relational databases
with a central server and distant clients. Data is loaded into client cache
based on queries executed on the server. These
queries have a special form called "universal relational query". The majority of
search queries to database can be expressed in such form. Besides, this form
allows us to analyze query correctness by checking lossless join property. A
subsequent query may be executed in client's local cache if we can determine
that the query result is entirely contained in the cache. For this we compare
truth spaces of the logical restrictions in new user's query and results of
the queries execution in cache. This method may be used to define lacking data
in cache and execute the query on server for this data only. Problem of data
actualizations in cache is not discussed in this paper. However, it can be
solved by cataloging of queries on server and their serving by triggers in
background mode.
\end{abstract}

\section *{Introduction}
In this paper we discuss the use of data views that are
cached on the client's computer. We assume client-server environment with
server based Relational Database (RDB). The cache stores query results in order
to provide maximum usage of saved data in subsequent queries.

@@

\section{Existing solutions overview and comparison}
One of the main research problems of queries optimization to database is the
construction of an optimal query plan. Queries are transformed without content
analysis of the database content and cache. In other cases, this information is
taken into account for calculation statistical estimations to improve physical
access to data. These problems are the subject of many studies, but they are
outside of our approach.

@@

\renewcommand{\refname}{References}
\bibliography{references}

### 2015-03-01 english_version/MAIS/theorem_1.tex
MAIS version was added. Codd OLAP citation was removed from all versions.

Condition  $F^{\ast}(t') = \n{TRUE}$ and statement 
\ref{proj_property_of_inclusion} imply the truth of the projection $F^{\ast}
[X^{\ast}]$ on a tuple $t'$, and consequently on $t''$, as the formula is defined at common attributes of these tuples. Furthermore, according to condition c), we have $F_v (t') = \n{TRUE} \Rightarrow F_v (t'') = \n{TRUE}$.
It means $t^{\ast} = t''[X^{\ast}] \in \pi_{X^{\ast}} (P_{v})$.
The theorem has been proven.
\end{proof}

>>>>

Condition  $F^{\ast}(t') = \n{TRUE}$ and statement 
\ref{proj_property_of_inclusion} imply the truth of the projection $F^{\ast}
[X_v]$ on a tuple $t'$, and consequently on $t''$, as the formula is defined at common attributes of these tuples. Furthermore, according to condition c), we have $F_v (t') = \n{TRUE} \Rightarrow F_v (t'') = \n{TRUE}$.
It means $t^{\ast} = t''[X^{\ast}] \in \pi_{X^{\ast}} (P_{v})$.
The theorem has been proven.
\end{proof}
